On a Alfvenicity of solar wind discontinuities

### 2024-09-28 article.qmd
update: comparison

---
title: On a Alfvenicity of solar wind discontinuities
authors:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
  - name: Sergei Kamaletdinov
    email: sergei2033@ucla.edu
    orcid: 0000-0002-2261-0331
    affiliation: University of California, Los Angeles
  - name: Xiaofei Shi
    email: sxf1698@ucla.edu
    orcid: 0000-0003-3367-5074
    affiliation: University of California, Los Angeles
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Marco Velli
    email: mvelli@ucla.edu
    orcid: 0000-0002-2381-3106
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
code-links:
  - text: Overleaf
    href: https://www.overleaf.com/project/668273f5d14067a22517615c
abstract: "Solar wind plasma flow is characterized by intense, large-amplitude current sheets, also known as solar wind discontinuities. These regions are believed to play a crucial role in magnetic reconnection, solar wind ion heating, and energetic particle scattering. Although solar wind discontinuities share several properties with the classical MHD model of rotational discontinuities, they exhibit more complex characteristics that include many kinetic properties, going beyond this model. One of the most puzzling properties of these discontinuities is their Alvenicity, which describes the relationship between Alfvén and plasma velocity jumps across discontinuities. Although the high correlation of these jumps suggests the rotational nature of discontinuities, the significant differences in jump amplitudes indicate the necessity of kinetic mechanisms to describe the stress balance within discontinuities. Spacecraft observations show that plasma thermal anisotropy alone may not sufficiently explain this difference and achieve stress balance. In this study, we present a theoretical model in which this difference is explained by the kinetics of interpenetrating ion beams crossing the discontinuity. Our model successfully describes the observed properties of discontinuities within the inner heliosphere."
---

@@

# References

- @steinhauerMultifluidModelOnedimensional2008
- @artemyevIonNongyrotropySolar2020
- @neukirchKineticModelsTangential2020
- @vaskoThinCurrentSheets2014

@@

>>>>

---
title: On a Alfvenicity of solar wind discontinuities
authors:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
  - name: Sergei Kamaletdinov
    email: sergei2033@ucla.edu
    orcid: 0000-0002-2261-0331
    affiliation: University of California, Los Angeles
  - name: Xiaofei Shi
    email: sxf1698@ucla.edu
    orcid: 0000-0003-3367-5074
    affiliation: University of California, Los Angeles
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Marco Velli
    email: mvelli@ucla.edu
    orcid: 0000-0002-2381-3106
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
code-links:
  - text: Overleaf
    href: https://www.overleaf.com/project/668273f5d14067a22517615c
  - text: Roam Research
    href: https://roamresearch.com/#/offline/Research/page/5EiGYXsXE
  - text: Zotero
    href: zotero://select/library/collections/DZHNUFNV
abstract: "Solar wind plasma flow is characterized by intense, large-amplitude current sheets, also known as solar wind discontinuities. These regions are believed to play a crucial role in magnetic reconnection, solar wind ion heating, and energetic particle scattering. Although solar wind discontinuities share several properties with the classical MHD model of rotational discontinuities, they exhibit more complex characteristics that include many kinetic properties, going beyond this model. One of the most puzzling properties of these discontinuities is their Alvenicity, which describes the relationship between Alfvén and plasma velocity jumps across discontinuities. Although the high correlation of these jumps suggests the rotational nature of discontinuities, the significant differences in jump amplitudes indicate the necessity of kinetic mechanisms to describe the stress balance within discontinuities. Spacecraft observations show that plasma thermal anisotropy alone may not sufficiently explain this difference and achieve stress balance. In this study, we present a theoretical model in which this difference is explained by the kinetics of interpenetrating ion beams crossing the discontinuity. Our model successfully describes the observed properties of discontinuities within the inner heliosphere."
---

@@

@@

|      | Harris Current Sheet                              | Yoon-Lui Current Sheet                               | Kan Current Sheet                        |
|-------------------|-------------------------------------------------------|--------------------------------------------------------|-----------------------------------------------------|
| **Magnetic Field** | $B_x(z) = B_0 \tanh(z/L)$ | $B_x(z) = B_0 \tanh \left(\frac{h}{L} \tan^{-1}(z/h)\right)$|$B_x^*(x^*, z^*)$ |
| **Number Density** | $n(z) = n_0 \text{sech}^2(z/L)$ | $n(z) = n_0 \text{sech}^2 \left(\frac{h}{L} \tan^{-1}(z/h)\right)$ | $n^*(x^*, z^*)$ |
| **Current Density** | $j_y(z) = B_0 \text{sech}^2(z/L) / (\mu_0 L)$ |$j_y(z) = \frac{B_0}{\mu_0 L} \frac{h^2}{z^2 + h^2} \text{sech}^2 \left(\frac{h}{L} \tan^{-1}(z/h)\right)$|                     |
| **Drift Velocity** |  |$V_y(z) = V_0 \frac{h^2}{(z^2 + h^2)}$ |                                       |
| **Special Feature** | Vlasov equilibrium, Maxwellian velocity distribution | Velocity shear important for thin current sheets       | Function form involves complex variables            |
